Pillar 2 - Topic Modeling

### 2019-01-16 Pillar 2 - Topic Modeling.Rmd
functions to visualize LDA output

```{r plot_tf_idf}
plot_tf_idf <- function(data, n_col = 5, plot_id = NULL){

@@

  ggsave(paste(plot_id, "_BP.jpeg", sep = ""), path = "Plots", width = 16, height = 8)
  print(g)

@@

  ggsave(paste(plot_id, "_WC.jpeg", sep = ""), path = "Plots", width = 16, height = 8)
  print(g)

@@

set.seed(123)
tf_idf_description %>%
  prepare_tf_idf_course %>%
  plot_tf_idf(plot_id = "Course_description")

set.seed(123)
tf_idf_overview %>%
  prepare_tf_idf_course %>%
  plot_tf_idf(plot_id = "Course_overview")

set.seed(123)
tf_idf_manual %>%
  prepare_tf_idf_course %>%
  plot_tf_idf(plot_id = "Course_manual")

@@

tf_idf_description %>%
  prepare_tf_idf_cluster %>%
  plot_tf_idf(plot_id = "Cluster_description")

tf_idf_overview %>%
  prepare_tf_idf_cluster %>%
  plot_tf_idf(plot_id = "Cluster_overview")

tf_idf_manual %>%
  prepare_tf_idf_cluster %>%
  plot_tf_idf(plot_id = "Cluster_manual")

@@

tf_idf_description %>%
  prepare_tf_idf_concentration %>%
  plot_tf_idf(plot_id = "Concentration_description")

tf_idf_overview %>%
  prepare_tf_idf_concentration %>%
  plot_tf_idf(plot_id = "Concentration_overview")

tf_idf_manual %>%
  prepare_tf_idf_concentration %>%
  plot_tf_idf(plot_id = "Concentration_manual")

@@

```{r, eval = FALSE}
LDA_description_10 <- LDA(d_description_cast, k = 10, control = list(seed = 123))
LDA_description_17 <- LDA(d_description_cast, k = 17, control = list(seed = 123))
LDA_description_25 <- LDA(d_description_cast, k = 25, control = list(seed = 123))

@@

```{r visualization LDA, eval = F}
visualize_LDA(LDA_SCI_2 , id_plot = "SCI, k = 2" )
visualize_LDA(LDA_SCI_5 , id_plot = "SCI, k = 5" )
visualize_LDA(LDA_SCI_10, id_plot = "SCI, k = 10")

visualize_LDA(LDA_cluster_10, id_plot = "Cluster, k = 10", facet = T)
visualize_LDA(LDA_cluster_17, id_plot = "Cluster, k = 17", facet = T)
visualize_LDA(LDA_cluster_25, id_plot = "Cluster, k = 25", facet = T)

>>>>

```{r plot_tf_idf}
plot_tf_idf <- function(data, n_col = 5, id_plot = NULL){

@@

  ggsave(paste(id_plot, "_BP.jpeg", sep = ""), path = "Plots", width = 16, height = 8)
  print(g)

@@

  ggsave(paste(id_plot, "_WC.jpeg", sep = ""), path = "Plots", width = 16, height = 8)
  print(g)

@@

set.seed(123)
tf_idf_description %>%
  prepare_tf_idf_course %>%
  plot_tf_idf(id_plot = "Course_description")

set.seed(123)
tf_idf_overview %>%
  prepare_tf_idf_course %>%
  plot_tf_idf(id_plot = "Course_overview")

set.seed(123)
tf_idf_manual %>%
  prepare_tf_idf_course %>%
  plot_tf_idf(id_plot = "Course_manual")

@@

tf_idf_description %>%
  prepare_tf_idf_cluster %>%
  plot_tf_idf(id_plot = "Cluster_description")

tf_idf_overview %>%
  prepare_tf_idf_cluster %>%
  plot_tf_idf(id_plot = "Cluster_overview")

tf_idf_manual %>%
  prepare_tf_idf_cluster %>%
  plot_tf_idf(id_plot = "Cluster_manual")

@@

tf_idf_description %>%
  prepare_tf_idf_concentration %>%
  plot_tf_idf(id_plot = "Concentration_description")

tf_idf_overview %>%
  prepare_tf_idf_concentration %>%
  plot_tf_idf(id_plot = "Concentration_overview")

tf_idf_manual %>%
  prepare_tf_idf_concentration %>%
  plot_tf_idf(id_plot = "Concentration_manual")

@@

```{r, cache = TRUE}
LDA_description_10 <- LDA(d_description_cast, k = 10, control = list(seed = 123))
LDA_description_17 <- LDA(d_description_cast, k = 17, control = list(seed = 123))
LDA_description_25 <- LDA(d_description_cast, k = 25, control = list(seed = 123))

@@

```{r}
# Bet Distribution
LDA_description_10 %>%
  prepare_data_LDA_beta %>%
  visualize_LDA_beta

# Gamma Distribution 1
LDA_description_10 %>%
  prepare_data_LDA_gamma(level = Cluster) %>%
  visualize_LDA_gamma1

# Gamma Distribution 2
LDA_description_10 %>%
  prepare_data_LDA_gamma(level = Cluster) %>%
  visualize_LDA_gamma2
```

```{r}
visualize_LDA <- function(data, level = Course, id_plot = "test"){

  # Beta distribution
  data %>% 
    prepare_data_LDA_beta %>%
    visualize_LDA_beta(id_plot = id_plot)

  # Gamma 1 distribution
  data %>% 
    prepare_data_LDA_gamma(level = !!ensym(level)) %>%
    visualize_LDA_gamma1(id_plot = id_plot)

  # Gamma 2 distribution
  data %>% 
    prepare_data_LDA_gamma(level = !!ensym(level)) %>%
    visualize_LDA_gamma2(id_plot = id_plot)

```{r visualization LDA, eval = F}
